Supplementary Information

### 2021-01-12 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd
closes #108

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_DBHx_analyzed=202 #n rows in climate_interactions_coefficients, excluding Hansley
n_DBHx_analyzed_sig=84
#precip:
n_DBHxP_RW_analyzed= 35
n_DBHxP_RW_sig=16
n_DBHxP_RW_sig_pos=n_DBHxP_RW_sig-4 #(exceptions: BEAL, TSCA, ACRU at HF, AFXY at HKK*) *pos response to precip in current growing season

n_DBHxP_BAI_analyzed= n_DBHxP_RW_analyzed
n_DBHxP_BAI_sig=15
n_DBHxP_BAI_sig_pos=10 #(exceptions: QURU & ACRU at HF, BEPA at NIO, QUVE at SCBI*,  AFXY at HKK*) *pos response to precip in current growing season
#T:
n_DBHxT_RW_analyzed= 32
n_DBHxT_RW_sig=11
n_DBHxT_RW_sig_neg=5 #notable that it's minority for RW, contrasting with slight majority neg for BAI

n_DBHxT_BAI_analyzed= n_DBHxT_RW_analyzed
n_DBHxT_BAI_sig=13
n_DBHxT_BAI_sig_neg=8 #mostly drought signal, including 4 species at CB
```

Interactive effects of climate and $DBH$ were found for `r n_DBHx_analyzed_sig` of the `r n_DBHx_analyzed` (`r round(n_DBHx_analyzed_sig/ n_DBHx_analyzed*100)`%) species-variable combinations for which they were tested. 
For precipitation variables, interactions were significant for `r n_DBHxP_RW_sig` of the `r n_DBHxP_RW_analyzed` (`r round(n_DBHxP_RW_sig/ n_DBHxP_RW_analyzed*100)`%) interactions with $RW$ as the growth metric (Fig. `r RW_interactions_all`) and for `r n_DBHxP_BAI_sig` of the `r n_DBHxP_BAI_analyzed` (`r round(n_DBHxP_BAI_sig/ n_DBHxP_BAI_analyzed*100)`%) with $BAI$ as the growth metric (Fig. `r BAI_interactions_all`).
The majority of these interactions were positive (`r round(n_DBHxP_RW_sig_pos/n_DBHxP_RW_sig*100)`% for $RW$; `r round(n_DBHxP_BAI_sig_pos/n_DBHxP_BAI_sig*100)`% for $BAI$), indicating that larger trees generally respond more positively (or less negatively) to precipitation or its frequency (Fig.  `r interactions_fig`).
Among the exceptions to this pattern (n=`r n_DBHxP_RW_sig-n_DBHxP_RW_sig_pos` for $RW$, `r n_DBHxP_BAI_sig-n_DBHxP_BAI_sig_pos` for $BAI$), only a minority (n=1 for $RW$, 2 for $BAI$) occurred in species responding positively to precipitation in the current growing season.

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_tested=37 #same for all metrics
n_best_model_RW=30
n_best_model_BAI=32
n_best_model_AGB=30
n_best_model_neg_RW=n_best_model_RW-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB)  90%
n_best_model_neg_BAI=n_best_model_BAI-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90.6%
n_best_model_neg_AGB=n_best_model_AGB-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90%
percent_neg_of_sig_trends="90-91%"
percent_sig_neg_trend_of_analyzed = "73-78%" 
#species consistently independent of year: PIEN and PILO at CB, CHTA at HKK, PIST3 at NM,

>>>>

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_DBHx_analyzed=204 #n rows in climate_interactions_coefficients, excluding Hansley
n_DBHx_analyzed_sig=88
#precip:
n_DBHxP_RW_analyzed= 36
n_DBHxP_RW_sig=16
n_DBHxP_RW_sig_pos=n_DBHxP_RW_sig-4 #(exceptions: BEAL, TSCA, ACRU at HF, AFXY at HKK*) *pos response to precip in current growing season

n_DBHxP_BAI_analyzed= n_DBHxP_RW_analyzed
n_DBHxP_BAI_sig=17
n_DBHxP_BAI_sig_pos=n_DBHxP_BAI_sig-7 #(exceptions: QURU & ACRU at HF, BEPA at NIO, QUVE & JUNI & CACO at SCBI*,  AFXY at HKK*) *pos response to precip in current growing season
#T:
n_DBHxT_RW_analyzed= 32
n_DBHxT_RW_sig=12
n_DBHxT_RW_sig_neg=5 #notable that it's minority for RW, contrasting with slight majority neg for BAI

n_DBHxT_BAI_analyzed= n_DBHxT_RW_analyzed
n_DBHxT_BAI_sig=15
n_DBHxT_BAI_sig_neg=9 #mostly drought signal, including 4 species at CB
```

Interactive effects of climate and $DBH$ were found for `r n_DBHx_analyzed_sig` of the `r n_DBHx_analyzed` (`r round(n_DBHx_analyzed_sig/ n_DBHx_analyzed*100)`%) species-variable combinations for which they were tested. 
For precipitation variables, interactions were significant for `r n_DBHxP_RW_sig` of the `r n_DBHxP_RW_analyzed` (`r round(n_DBHxP_RW_sig/ n_DBHxP_RW_analyzed*100)`%) interactions with $RW$ as the growth metric (Fig. `r RW_interactions_all`) and for `r n_DBHxP_BAI_sig` of the `r n_DBHxP_BAI_analyzed` (`r round(n_DBHxP_BAI_sig/ n_DBHxP_BAI_analyzed*100)`%) with $BAI$ as the growth metric (Fig. `r BAI_interactions_all`).
The majority of these interactions were positive (`r round(n_DBHxP_RW_sig_pos/n_DBHxP_RW_sig*100)`% for $RW$; `r round(n_DBHxP_BAI_sig_pos/n_DBHxP_BAI_sig*100)`% for $BAI$), indicating that larger trees generally respond more positively (or less negatively) to precipitation or its frequency (Fig.  `r interactions_fig`).
Among the exceptions to this pattern (n=`r n_DBHxP_RW_sig-n_DBHxP_RW_sig_pos` for $RW$, `r n_DBHxP_BAI_sig-n_DBHxP_BAI_sig_pos` for $BAI$), only a minority (n=1 for $RW$, 4 for $BAI$) occurred in species responding positively to precipitation in the current growing season.

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan12)
n_tested=37 #same for all metrics
n_best_model_RW=30
n_best_model_BAI=32
n_best_model_AGB=30
n_best_model_neg_RW=n_best_model_RW-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB)  90%
n_best_model_neg_BAI=n_best_model_BAI-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90.6%
n_best_model_neg_AGB=n_best_model_AGB-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90%
percent_neg_of_sig_trends="90-91%"
percent_sig_neg_trend_of_analyzed = "73-78%" 
#species consistently independent of year: PIEN and PILO at CB, CHTA at HKK, PIST3 at NM,
